WORCS: A Workflow for Open Reproducible Code in Science

### 2020-11-03 paper/reviews_ds.Rmd
R1 C12: Add docker image

Response: We agree that synthetic data generation is exciting, but feel obliged to clarify that this is **not** a novel contribution of the present paper nor R-package. 
As indicated in the paper, we use the algorithm by Nowok and colleagues,
who explain the details of the method.
We re-implemented the method in the `worcs` package because the `synthpop` package
is rarely maintained (e.g., one of our pull requests took almost 10 months to be accepted),
and because we wanted a more flexible, customizable interface.

@@

\RC{Docker is deemed as complicated for novice users, but the setup vignete looks quite complex to me as well. Wouldn't a Docker container with worcs installed be easier to use? Maybe these aspects would be better highlighted in a user evaluation.}

Response: Thank you for this thoughtful suggestion. We explained better why `renv` is more user friendly (because it builds upon the "normal" package workflow of R users). For users familiar with Docker, we have published an image on Docker Hub with all requirements of worcs installed and a Docker specific setup vignette, that is much shorter and given that you know how to use Docker easier.
\Assignment{AP, AB}
\WorkInProgress
\Medium

>>>>

Response: We agree that synthetic data generation is exciting, but feel obliged to clarify that this is **not** a novel contribution of the present paper nor R-package. 
As indicated in the paper, we use the algorithm by Nowok and colleagues,
who explain the details of the method.
We re-implemented the method in the `worcs` package because the `synthpop` package
is rarely maintained (e.g., [one of our pull requests](https://github.com/bnowok/synthpop/pull/12) took almost 10 months to be accepted),
and because we wanted a more flexible, customizable interface.

@@

\RC{C12: Docker is deemed as complicated for novice users, but the setup vignete looks quite complex to me as well. Wouldn't a Docker container with worcs installed be easier to use? Maybe these aspects would be better highlighted in a user evaluation.}

Response: We thank the Reviewer for this thoughtful suggestion.
To address this comment, 
we have published an image on Docker Hub with all requirements of `worcs` installed,
and added a Docker-specific setup vignette to the package and website, which is referenced in the Setup pagragraph:

> Before you can use the `R` implementation of the WORCS workflow,
you have to install the required software.
This 30 minute procedure is documented
in [the setup vignette](https://cjvanlissa.github.io/worcs/articles/setup.html).
After setting up your system, you can use `worcs` for all of your
projects.
Alternatively, Docker users can follow [the stetup with Docker vignette](https://cjvanlissa.github.io/worcs/articles/docker.html).

\Assignment{AP, AB}
\Done
\Medium
